04_application

### 2020-01-21 chapters/04_application.Rmd
revert to avg daily boardings

@@

@@

>>>>

### Metro Transit Data

### Covariates

@@

The baseline Poisson regression can be fit easily in Stan. This simplest model in this case study can be written

\begin{align}
Y_i & \sim \text{Poisson}(E_i\lambda_i) \\
\eta_i  = log(\lambda_i) & = \beta_0 + \sum_{k=1}^{19}x_k^T\beta_k \\
\beta_0, \beta & \sim \text{Normal}(0, 1) \\
\end{align}

where $Y_i$ is the number of boardings in census block group $i$ in 2017, $E_i$ is the number of bus stops made in block group $i$ in 2017, and parameter vector $x$ corresponds to the covariates discussed above. **Figure ...** shows this model written in Stan.

```{r}
# FIND A BETTER WAY TO PRINT THIS
writeLines(readLines("~/Documents/honors/honors-project/stan/poisson.stan"))
```

@@

The model above does a decent job predicting ridership but there are many possible improvements. One shortcoming of the simplest Poisson model is that the normal priors on $\beta$ make it challenging to determine which coefficients are truly significantly different from 0. This is where the regularized horseshoe prior comes into play.

This model can be expressed in Stan as pictured in **Figure...**. The Stan program for this model was adapted from **Vehtari..**.

```{r}
writeLines(readLines("~/Documents/honors/honors-project/stan/poisson_horseshoe.stan"))
```
